*flippant* -- An R package for the automated analysis of dithionite scramblase

### 2016-03-20 inst/manuscript/manuscript.rmd
Adapt funding statement to QNRF-preferred wording;

#Funding
J.G., R.J.C. and the Proteomics Core at WCMC-Q are supported by ``Biomedical 
Research Program'' funds at Weill Cornell Medical College in Qatar, a program 
funded by Qatar Foundation. B.P. was supported by a grant from Qatar National 
Research Fund’s National Priority Research Program (5-669-1-112) to J.G. and
A.K.M., as well as by the Austrian Science Fund (FWF), project J3686-B21.

>>>>

#Funding
J.G., R.J.C. and the Proteomics Core at WCMC-Q are supported by ``Biomedical 
Research Program'' funds at Weill Cornell Medical College in Qatar, a program 
funded by Qatar Foundation. This study was made possible by NPRP grant
5-669-1-112 from the Qatar National Research Fund (a member of Qatar 
Foundation).The statements made herein are solely the responsibility of the
authors. B.P. was also supported by the Austrian Science Fund (FWF), project
J3686-B21.
